Effects of the body force on the evacuation dynamics

### 2020-01-01 paper.tex
mas correcciones de gramatica en la parte de resultados

In Fig \ref{degree_dens} we show the mean degree as a function of the global density for different $k$ values. When the density is low,  the degree is zero because the pedestrians do not touch each other. When the density is around 4.5, a few pedestrians start to touch each other increasing the mean degree. As the density increases, the mean degree increases too until reaching an asymptotic behavior in degree six. When the degree is six, it corresponds to the densest packing possible for identical hard circles, the result is a hexagonal packing arrangement.\\

It is important to notice that in Fig. \ref{degree_dens} for a given value of density, the stiffer the pedestrians, the higher the degree. A higher degree means more friction force which is the cause of the reduction of the flow. In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree. This is the reason why in bottleneck pedestrians evacuate faster as they become stiffer while in corridor pedestrian\textsc{\char13}s flow is lower as they become stiffer.\\

The mean overlap increases as the global density increases (see Fig. \ref{overlap_dens}) and the higher the stiffness the lower the overlap. This result is similar to the overlap vs. the desired velocity obtained for bottleneck geometry. The higher the value of $k$ the higher the repulsion of pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
\caption[width=0.47\columnwidth]{\ref{degree_dens} mean degree as a function of the global density for different $k$ values. \label{overlap_dens} mean overlap as a function of the global density. The mean values are averages over all the pedestrians and over time once the system reaches the stationary state. Both measurements correspond to corridor geometry with desired velocity $v_d=1$.}
\label{network_corridor}
\end{figure}

As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck but increases the mean degree in a corridor. In Fig.\ref{network_corridor} it shown the network associated with the corridor at a particular timestep and a particular global density. Fig. \ref{network_d6_kn0} corresponds to $k=0$ while Fig. \ref{network_d6_knE5} corresponds to $k=1.2$~E5. This is an example to show how increasing the stiffness increases the number of contacts between pedestrians. Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$. \\

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor. The lines that connect the nodes (pedestrians) represent the contact between them. The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her). The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. \ref{network_d6_kn0} corresponds to a simulation without body force and \label{network_d6_knE5} corresponds to a simulation with $k=1.2$~E5.}
\label{network_corridor}
\end{figure}

The increment of the clusterization is responsible for the reduction of the flow. In the corridor geometry, the crowd gets more clusterized if the pedestrians become stiffer. We studied the network properties of the contact graph arising from the positions $(x,y)$ of every the pedestrians. We found that a good descriptor to exhibit the clusterization is the number of triangles per node. A triangle is defined as a structure composed of three nodes all in contact with each other. In Fig. \ref{triangles} we show the triangles per node as a function of the global density for different stiffness values $k$. This descriptor allows to distinguish states with the same global density but different stiffness levels. In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the degree of clustering of the system even better than the mean degree. \\

This result is consistent with the results obtained in Ref. \cite{pugnaloni_2013} where they explore several topological and geometric descriptors capable of properly describing granular systems with different stiffness. While our study system is self-propelled, there are analogies with the system studied in Ref. Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\

>>>>

Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k$ values. When the density is low,  the degree is zero because the pedestrians do not touch each other. When the density is around 4.5, a few pedestrians start to touch each other increasing the mean degree. As the density increases, the mean degree increases too until reaching an asymptotic behavior in degree six. When the degree is six, it corresponds to the densest packing possible for identical hard circles, the result is a hexagonal packing arrangement.\\

It is important to notice that in Fig. \ref{degree_dens} for a given value of density, the stiffer the pedestrians, the higher the degree. A higher degree means more friction force which is the cause of the reduction of the flow. In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree. This is the reason why in a bottleneck, pedestrians evacuate faster as they become stiffer while in a corridor the pedestrian\textsc{\char13}s flow is lower as they become stiffer.\\

The mean overlap increases as the global density increases (see Fig. \ref{overlap_dens}) and the higher the stiffness the lower the overlap. This result is similar to the overlap vs. desired velocity obtained for bottleneck geometry. The higher the value of $k$ the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k$ values. (b) mean overlap as a function of the global density. The mean values are averages over all the pedestrians and over time once the system reaches the stationary state. Both measurements correspond to corridor geometry with desired velocity $v_d=1$.}
\label{network_corridor}
\end{figure}

As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck but increases the mean degree in a corridor. In Fig.~\ref{network_corridor} it shown the contact network corresponding to the corridor at a particular timestep and a particular global density. Fig.~\ref{network_d6_kn0} corresponds to $k=0$ while Fig. \ref{network_d6_knE5} corresponds to $k=1.2$~E5. This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity). Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$. \\

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor. The lines that connect the nodes (pedestrians) represent the contact between them. The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her). The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. (a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k=1.2$~E5.}
\label{network_corridor}
\end{figure}

The increment of the clusterization is responsible for the reduction of the flow. In the corridor geometry, the crowd gets more clusterized if the pedestrians become stiffer. We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian. We found that a good descriptor to exhibit the connectivity is the number of triangles per node. A triangle is defined as a structure composed of three nodes all in contact with each other. Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k$. This descriptor allows to distinguish states with the same global density but different stiffness levels. In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree. \\

This result is consistent with the results obtained in Ref.~\cite{pugnaloni_2013} where the authors explore several topological and geometric descriptors capable of properly describing granular systems with different stiffness. While our study system is self-propelled, there are analogies with the system studied in Ref.~\cite{pugnaloni_2013} Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\
